\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Use math mode for mu and sigma.
Maybe this should be \mu and \sigma.
Fix Study 1 technical expertise summary.
I got the counts from sessions/pre/participant-summaries.txt:
	has never heard of Tor or used it: P2, P3, P4, P12, P13, P14, P15, P16
	heard of tor but has not used it:  P1, P6, P7, P9, P13
	used tor before: P8, P10, P11, P5
The sentence used to say,
	5 had previously heard of Tor but not used it, while and 5 had used Tor previously.

Out of our 16 participants, ages ranged from 20 to 62
(mu= 24.5, sigma = 12.6). 53.3\% were male. 
93.3\% of our participants had at least
a college education. 5 had previously heard of Tor but not used it, while 
and 5 had used Tor previously.

@@

Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to 68
(mu = 28.9, sigma = 12). 56.8\% were male and 
84.8\% of our participants had at least a college education.

>>>>

Out of our 16 participants, ages ranged from 20 to~62
($\mbox{mu} = 24.5$, $\mbox{sigma} = 12.6$). 53.3\% were male. 
93.3\% of our participants had at least
a college education.
4 participants had used Tor before,
5 had heard of Tor but not used it,
and the remaining 8 had never heard of Tor nor used it.

@@

Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
recruited from Craigslist. Ages ranged from 18 to 68
($\mbox{mu} = 28.9$, $\mbox{sigma} = 12$). 56.8\% were male and 
84.8\% of our participants had at least a college education.
